sentiment analysis

# In this project, I used a lexical analyzer - 'bing'. The dataset I used was provided by the R package 'janeaustenr'. I visualized the words present in the book "Persuasion" based on their corrosponding positive and negative scores.


```{r}
library(tidytext)
sentiments
```
Three lexicons:
a. AFINN (model scores the words in a range from -5 to 5)
b. bing (classifies the sentiment into a binary category of negative or positive)
c. loughran (performs analysis of the shareholder’s reports)

```{r}
get_sentiments("bing")
```
```{r}
library(janeaustenr)
library(stringr)
library(tidytext)
library(dplyr)

tidy_data <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
tidy_data
```

```{r}
unique(tidy_data$book)
```

```{r}
positive_senti <- get_sentiments("bing") %>%
 filter(sentiment == "positive")

tidy_data %>%
 filter(book == "Persuasion") %>%
 semi_join(positive_senti) %>%
 count(word, sort = TRUE)
```

```{r}
library(tidyr)
bing <- get_sentiments("bing")
Persuasion_sentiment <- tidy_data %>%
 inner_join(bing) %>%
 count(book = "Persuasion" , index = linenumber %/% 80, sentiment) %>%
 spread(sentiment, n, fill = 0) %>%
 mutate(sentiment = positive - negative)
```

```{r}
library(ggplot2)

ggplot(Persuasion_sentiment, aes(index, sentiment, fill = book)) +
 geom_bar(stat = "identity", show.legend = TRUE) +
 facet_wrap(~book, ncol = 2, scales = "free_x")
```

```{r}
counting_words <- tidy_data %>%
 inner_join(bing) %>%
 count(word, sentiment, sort = TRUE)
head(counting_words)
```
```{r}
counting_words %>%
 filter(n > 150) %>%
 mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
 mutate(word = reorder(word, n)) %>%
 ggplot(aes(word, n, fill = sentiment))+
 geom_col() +
 coord_flip() +
 labs(y = "Sentiment Score")
```
```{r}
library(reshape2)
library(wordcloud)
tidy_data %>%
 inner_join(bing) %>%
 count(word, sentiment, sort = TRUE) %>%
 acast(word ~ sentiment, value.var = "n", fill = 0) %>%
 comparison.cloud(colors = c("red", "dark green"),
          max.words = 100)
```

